SunPy - Python for Solar Physics

### 2014-08-28 3-2-HEK.tex
HEK text cleaned up a bit

HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
and \texttt{or}). The ability to use comparison and logical operators on HEK attributes allows 
the construction of queries of arbitrary complexity.
For the query in Listing \ref{code:hek:or} returns
returns flares with helioprojective x coordinates west of 50 arcseconds or 
those that have a peak flux above 1000.0 in units defined by the FRM.

>>>>

HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
and \texttt{or}). The ability to use comparison and logical operators on HEK attributes allows 
the construction of queries of arbitrary complexity.
For the query in Listing \ref{code:hek:or} returns
returns flares with helio-projective $x$-coordinates west of 50 arcseconds or 
those that have a peak flux above 1000.0 (in units defined by the FRM).
